SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-06 scipy-1.0/paper.tex
Added a final summary paragraph to the language choices subsection along with appropriate references for discussion of JIT compilers.

>>>>

Therefore, the relative abundance of different programming languages
in the SciPy library results from a combination of the usage of powerful performance
enhancing languages that interact well with Python (i.e., Cython), and
the usage of languages (and their libraries) that have proven reliable
and performant over many decades. The position that SciPy occupies
near the foundation of the scientific Python ecosystem is such that
adoption of new languages or major dependencies is generally unlikely--our
choices are strongly driven by long-term stability. GPU acceleration,
new transpiling libraries, and the latest JIT compilation approaches
(i.e., Numba\cite{Lam:2015:NLP:2833157.2833162}) are very powerful, but currently fall outside the remit
of the main SciPy library. That said, we have recently increased our
efforts to support compatibility with some of these options, and having
our full test suite pass with the PyPy JIT compiler\cite{Bolz:2009:TMP:1565824.1565827}
is now a requirement in our development workflow.
